### 2014-05-05 doc/thesis/cases.tex
Finished the porting of typing Lua standard libraries

@@

@@

@@

@@

@@

>>>>

\begin{enumerate}
\item coroutine.create (f) :
$(\TopStar \rightarrow \TopStar) \times \TopStar \rightarrow Thread \times \NilStar$
\item coroutine.resume (co [, val1, ···]) :
$Thread \times
\TopStar \rightarrow
(\True \times \AnyStar) \cup
(\False \times \String \times \NilStar)$
\item coroutine.running () :
$\TopStar \rightarrow Thread \times \Boolean \times \NilStar$
\item coroutine.status (co) :
$Thread \times \TopStar \rightarrow \String \times \NilStar$
\item coroutine.wrap (f) :
$(\TopStar \rightarrow \TopStar) \times
\TopStar \rightarrow
(\TopStar \rightarrow \TopStar) \times
\NilStar$ 
\item coroutine.yield (···) :
$\TopStar \rightarrow \NilStar$
\end{enumerate}

@@

\begin{enumerate}
\item require (modname) :
$\String \times \TopStar \rightarrow \{\Any:\Any\} \times \NilStar$
\\
The function \textbf{require} returns exactly the same value that is
returned by loading \textbf{modname}.
However, if the returned value is $\Nil$, this value is
converted to $\True$.
\item package.config : $\String$
\item package.cpath : $\String$
\item package.loaded : $\{\String:\{\Any:\Any\}\}$
\item package.loadlib (libname, funcname) :
$\String \times
\String \times
\TopStar \rightarrow
(\True \times \NilStar) \cup
(\Nil \times \String \times \NilStar)$
\item package.path : $\String$
\item package.preload : $\{\String:\{\Any:\Any\}\}$
\item package.searchers : $\{\Number:\TopStar \rightarrow \TopStar\}$
\item package.searchpath (name, path [, sep [, rep]]) :
$\String \times
\String \times
(\String \cup \Nil) \times
(\String \cup \Nil) \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\Nil \times \String \times \NilStar)$
\end{enumerate}

@@

\begin{enumerate}
\item bit32.arshift (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.band (···) :
$\Number{*} \rightarrow \Number \times \NilStar$
\item bit32.bnot (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.bor (···) :
$\Number{*} \rightarrow \Number \times \NilStar$
\item bit32.btest (···) :
$\Number{*} \rightarrow \Number \times \NilStar$
\item bit32.bxor (···) :
$\Number{*} \rightarrow \Number \times \NilStar$
\item bit32.extract (n, field [, width]) :
$\Number \times
\Number \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$
\item bit32.replace (n, v, field [, width]) :
$\Number \times
\Number \times
\Number \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$
\item bit32.lrotate (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.lshift (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.rrotate (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.rshift (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\end{enumerate}

@@

\begin{enumerate}
\item io.close ([file]) :
$(Userdata \cup \Nil) \times
\TopStar \rightarrow
(\Boolean \times \NilStar) \cup
(\Nil \times \String \times \NilStar) \cup
((\True \cup \Nil) \times \String \times \Number \times \NilStar)$
\\
Returns $((\True \cup \Nil) \times \String \times \Number \times \NilStar)$
when the file handle was created with \textbf{io.popen}.
\item io.flush () :
$\TopStar \rightarrow \Boolean \times \NilStar$
\item io.input ([file]) :
$(\String \cup Userdata \cup \Nil) \times
\TopStar \rightarrow
Userdata \times
\NilStar$
\item io.lines ([filename ···]) :
$(\String \cup Userdata \cup \Nil) \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\Nil \times \NilStar)$
\\
In fact, this function returns an iterator. Need to check the return type.
\item io.open (filename [, mode]) :
$\String \times
(``r" \cup ``w" \cup ``a" \cup
``r+" \cup ``w+" \cup ``a+" \cup
``rb" \cup ``wb" \cup ``ab" \cup
``r+b" \cup ``w+b" \cup ``a+b" \cup
\Nil) \times
\TopStar \rightarrow
(Userdata \times \NilStar) \cup
(\Nil \times \String \times \Number \times \NilStar)$
\item io.output ([file]) :
$(\String \cup Userdata \cup \Nil) \times
\TopStar \rightarrow
Userdata \times
\NilStar$
\item io.popen (prog [, mode]) :
$\String \times
(``r" \cup ``w" \cup \Nil) \times
\TopStar \rightarrow
(Userdata \times \NilStar) \cup
(\Nil \times \String \times \Number \times \NilStar)$
\item io.read (···) :
$(``*n" \cup ``*a" \cup ``*l" \cup ``*L" \cup \Number){*} \rightarrow
(\String \cup \Number){*}
$
\item io.tmpfile () :
$\TopStar \rightarrow Userdata \times \NilStar$
\item io.type (obj) :
$\Top \times \TopStar \rightarrow (``file" \cup ``closed\;file" \cup \Nil) \times \NilStar$
\item io.write (···) :
$(\String \cup \Number){*} \rightarrow
(Userdata \times \NilStar) \cup
(\Nil \times \String \times \Number \times \NilStar)$
\item file:close () : ?
\item file:flush () : ?
\item file:lines (···) : ?
\item file:read (···) : ?
\item file:seek ([whence [, offset]]) : ?
\item file:setvbuf (mode [, size]) : ?
\item file:write (···) : ?
\end{enumerate}

@@

\begin{enumerate}
\item os.clock () :
$\TopStar \rightarrow \Number \times \NilStar$
\item os.date ([format [, time]]) :
$(\String \cup \Nil) \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\{``year":\Number,\;
   ``month":\Number,\;
   ``day":\Number,\;
   ``hour":\Number,\;
   ``min":\Number,\;
   ``sec":\Number,\;
   ``wday":\Number,\;
   ``yday":\Number,\;
   ``isdst":\Boolean \} \times \NilStar)$
\\
Returns a table when \textbf{format} contains ``\textbf{*t}''.
\item os.difftime (t2, t1) :
$\Number \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$
\\
Returns \textbf{t2} when \textbf{t1} is $\Nil$.
\item os.execute ([command]) :
$(\String \cup \Nil) \times
\TopStar \rightarrow
(\Boolean \times \NilStar) \cup
((\True \cup \Nil) \times \String \times \Number \times \NilStar)$
\\
Returns just a Boolean when \textbf{command} is $\Nil$.
This Boolean means whether there is a shell available.
Returns $\True \times \String \times \Number \times \NilStar$ when
\textbf{command} terminated successfully.
Returns $\Nil \times \String \times \Number \times \NilStar$ when
\textbf{command} did not terminate sucessfully.
\item os.exit ([code [, close]]) :
$(\Number \cup \Boolean \cup \Nil) \times
\Top \times
\TopStar \rightarrow
\NilStar$
\item os.getenv (varname) :
$\String \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\Nil \times \NilStar)$
\item os.remove (filename) :
$\String \times
\TopStar \rightarrow
(\True \times \NilStar) \cup
(\Nil \times \String \times \Number \NilStar)$
\item os.rename (oldname, newname) :
$\String \times
\String \times
\TopStar \rightarrow
(\True \times \NilStar) \cup
(\Nil \times \String \times \Number \NilStar)$
\item os.setlocale (locale [, category]) :
$(\String \cup \Nil) \times
(``all" \cup
``collate" \cup
``ctype" \cup
``monetary" \cup
``numeric" \cup
``time" \cup
\Nil) \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\Nil \times \NilStar)$
\item os.time ([table]) :
$(\{``year":\Number,\;
   ``month":\Number,\;
   ``day":\Number,\;
   ``hour":(\Number \cup \Nil),\;
   ``min":(\Number \cup \Nil),\;
   ``sec":(\Number \cup \Nil),\;
   ``wday":(\Number \cup \Nil),\;
   ``yday":(\Number \cup \Nil),\;
   ``isdst":(\Boolean \cup \Nil) \} \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$
\item os.tmpname () :
$\TopStar \rightarrow \String \times \NilStar$
\end{enumerate}

@@

\begin{enumerate}
\item debug.debug () : ?
\item debug.gethook ([thread]) : ?
\item debug.getinfo ([thread,] f [, what]) : ?
\item debug.getlocal ([thread,] f, local) : ?
\item debug.getmetatable (value) : ?
\item debug.getregistry () : ?
\item debug.getupvalue (f, up) : ?
\item debug.getuservalue (u) : ?
\item debug.sethook ([thread,] hook, mask [, count]) : ?
\item debug.setlocal ([thread,] level, local, value) : ?
\item debug.setmetatable (value, table) : ?
\item debug.setupvalue (f, up, value) : ?
\item debug.setuservalue (udata, value) : ?
\item debug.traceback ([thread,] [message [, level]]) : ?
\item debug.upvalueid (f, n) : ?
\item debug.upvaluejoin (f1, n1, f2, n2) : ?
\end{enumerate}
